% !TeX root = ../main.tex
% \graphicspath{ {./images/} }
\section{Deep Neural Network}

Deep Neural Network is considered a powerful machine learning model as more and more breakthroughs and state-of-the-art results have been achieved in recent years. By constructing neurons in a deep neural network model, networks can learn non-linear relationships between input features and decompose complicated data to figure out hidden patterns \cite{DNN_2015}. Therefore, Deep learning methods are involved in various popularity prediction models for learning the representations and capturing the underlying dependencies. Graph neural network is also a kind of deep neural network. 

Since we have introduced and briefly listed several related works in the previous section, we would only share two studies related to other deep learning techniques here.

\cite{inproceedings} proposes a multimodal variational encoder-decoder (MMVED) framework to predict the popularity of videos. In this study, a long-short term memory (LSTM) decoder is implemented to be part of the decoder of MMVED for capturing temporal dynamics of popularity evolution.

DFTC is proposed in \cite{Liao_Xu_Li_Huang_Liu_Li_2019} aiming at capturing different patterns of popularity prediction in different stages of life cycles of online articles. Given the number of days after a photo was shared, DFTC can predict a sequence of popularity in matrix form. Recurrent neural network (RNN) and convolutional neural network (CNN) techniques are adopted to DFTC to learn the temporal dynamic of popularity. In addition, hierarchical attention network is also involved in DFTC model and learn the representations of content features.

